HO unification from object language to meta language

### 2024-04-05 paper/main.tex
typo

\newcommand{\linkbeta}{\texttt{link-}\ensuremath{\beta}\xspace}
\newcommand{\linketa}{\texttt{link-}\ensuremath{\eta}\xspace}

@@

TODO: What is commit-links and complete-mapping?, maybe complete-mapping can be
hidden in the code rendering?

@@

\subsection{Compilation}\label{sec:etacomp}

@@

@@

\newcommand{\progressetaleft}{\emph{progress-$\eta$-left}\xspace}
\begin{definition}[\progressetaleft]\label{def:progressetaleft}
A link \linketaM{\Gamma}{X}{T} is removed from \linkStore when
$X$ becomes rigid. There are two cases:
\begin{enumerate}
  \item if $X = a$ or $X = y$ or $X = f \appsep a_1\ldots a_n$
    we unify the $\eta$-expansion of the $X$ with $T$, that is we run
    $\lambda x.X \appsep x\Ue{} T$  (under
    the context $\Gamma$)
    \noteE[inline]{where y comes from? $X = y$: $y$ is in the ctx of X}
    \item if $X = \lambda x.t$ we run $X \Ue{} T$.
\end{enumerate}
\end{definition}

@@

\noteD[inline]{Should we proove simulation fidelity for \linketa insertion?}

@@

\noteE[inline]{dire che preserviamo l'invariante che tutte le variable sono fully-applied
}
\section{Handling of \maybebeta}\label{sec:beta}

@@

\subsection{Compilation}

@@

@@

\begin{definition}[\progBetaLL]
  Given a substitution $\sigma$ and a \linkbeta \linkbetaM{\Gamma}{T}{\rhsBeta}
  such that $\sigma t_1$ is a name, say $t$, and $t\notin s_1\dots s_n$. If $m =
  0$, then the \linkbeta is removed and \lhs is unified with \rhsBetaHead.
  If $m > 0$, then the \linkbeta is replaced by a refined version
  $\linkbetaM{\Gamma}{T}{Y_{s_1\dots s_n,t}\appsep t_2\dots t_m}$ with reduced
  list of arguments and $Y$ being a fresh variable. Moreover, the new \linkbeta,
  \linketaM{\Gamma}{X_{s_1\dots s_n}}{\lambda x.Y_{s_1\dots s_n,x}} is added to 
  \linkStore.

@@

\noindent
Initially the \linkbeta \rhs is a variable $D$ applied to the $E_x$.
The first unification problem results in $\sigma =
\{A \mapsto \lambda x.x\}$. In turn this instantiation
triggers $\linkStore_1$ by \progressetaleft 
and $E$ is assigned to $\lambda x.x$.
Under this substitution the \linkbeta becomes
\linkbetaM{x}{C_x}{(D \appsep x)}, and by \progBetaLL
it is replaced with the link:
\linketaM{}{E}{\lambda x.D_x}, while $C_x$ is unified with $D_x$. The second unification
problem assigns $f$ to $B$, that in turn activates
the second \linketa ($f$ is assigned to $C$), and then all the remaining links
are solved. The final \Ho substitution is $\sigma = \{A _{} \mapsto \lambda x.x, 
B _{} \mapsto f, C _{x} \mapsto (f\appsep x), 
D _{} \mapsto f, E _{x} \mapsto x, F _{x} \mapsto C_{x} \}$ and is decompiled into $\rho = \{X \mapsto \lambda x.x,
Y \mapsto f\}$.
\noteE{alla fine non si usa anche la regola beta-rigid-head?}
\noteD{nope. Si risolve tutto by \progBetaLL}

@@

\subsection{Relaxing \cref{lemma:keep-fidelity}}

@@

>>>>

\newcommand{\linkMacro}[1]{\ensuremath{#1}\texttt{-link}\xspace}

\newcommand{\linkbeta}{\linkMacro{\beta}}
\newcommand{\linketa} {\linkMacro{\eta}}

@@

\noteE{What is commit-links and complete-mapping?}

@@

\subsection{Compilation and decompilation}\label{sec:etacomp}

@@

\noteD[inline]{Dire della commit-links: intuizione fa round trip}

@@

\newcommand{\progressetaleft}{\emph{progress-$\eta$-left}\xspace}
\begin{definition}[\progressetaleft]\label{def:progressetaleft}
A link \linketaM{\Gamma}{X}{T} is removed from \linkStore when
$X$ becomes rigid. Let $y\in\Gamma$, there are two cases:
\begin{enumerate}
  \item if $X = a$ or $X = y$ or $X = f \appsep a_1\ldots a_n$
    we unify the $\eta$-expansion of $X$ with $T$, that is we run
    $\lambda x.X \appsep x\Ue{} T$
    \item if $X = \lambda x.t$ we run $X \Ue{} T$.
\end{enumerate}
\end{definition}

@@

\noteD[inline]{Proove simulation fidelity, dicendo che \progressetaright è inutile}

@@

% \noteE[inline]{dire che preserviamo l'invariante che tutte le variable sono fully-applied
% }
\section{Handling of \maybebeta}\label{sec:beta}

@@

\subsection{Compilation and decompilation}

@@

\noteD[inline]{Dire della commit-links: intuizione non devono esserci beta per corollary}

@@

\begin{definition}[\progBetaLL]
  Given a substitution $\sigma$ and a \linkbeta \linkbetaM{\Gamma}{T}{\rhsBeta}
  such that $\sigma t_1$ is a name, say $t$, and $t\notin s_1\dots s_n$. If $m =
  0$, then the \linkbeta is removed and \lhs is unified with \rhsBetaHead.
  If $m > 0$, then the \linkbeta is replaced by a refined version
  $\linkbetaM{\Gamma}{T}{Y_{s_1\dots s_n,t}\appsep t_2\dots t_m}$ with reduced
  list of arguments and $Y$ being a fresh variable. Moreover, the new link
  \linketaM{\Gamma}{X_{s_1\dots s_n}}{\lambda x.Y_{s_1\dots s_n,x}} is added to 
  \linkStore.

@@

\noindent
Initially the \linkbeta \rhs is a variable $D$ applied to the $E_x$.
The first unification problem results in $\sigma =
\{A \mapsto \lambda x.x\}$. In turn this instantiation
triggers $\linkStore_1$ by \progressetaleft 
and $E_x$ is assigned to $x$.
Under this substitution the \linkbeta becomes
\linkbetaM{x}{C_x}{(D \appsep x)}, and by \progBetaLL
it is replaced with the link:
\linketaM{}{E}{\lambda x.D_x}, while $C_x$ is unified with $D_x$. The second unification
problem assigns $f$ to $B$, that in turn activates
the second \linketa ($f$ is assigned to $C$), and then all the remaining links
are solved. The final \Ho substitution is $\sigma = \{A _{} \mapsto \lambda x.x, 
B _{} \mapsto f, C _{x} \mapsto (f\appsep x), 
D _{} \mapsto f, E _{x} \mapsto x, F _{x} \mapsto C_{x} \}$ and is decompiled into $\rho = \{X \mapsto \lambda x.x,
Y \mapsto f\}$.

@@

\subsection{Relaxing \cref{lemma:keep-fidelity} : tobe renamed}

@@

\noteD[inline]{Dire qualcosa sulla commit-links}
